%Basics
\documentclass[aps, prl, reprint, a4paper, english, 12pt, twocolumn]{revtex4}
\usepackage[utf8]{inputenc}
\usepackage{babel}

%Symbols and scientifics
\usepackage{amsmath}
\usepackage{commath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{mathtools}
\usepackage{siunitx}
\sisetup{
per-mode = fraction ,
round-mode = figures ,
round-precision = 3 ,
scientific-notation = engineering ,
output-decimal-marker = {.} ,
exponent-product = \times ,
separate-uncertainty = true ,
uncertainty-separator = \ ,
output-product = \cdot ,
quotient-mode = fraction ,
range-phrase = - ,
range-units =  single ,
inter-unit-product = \ensuremath{{\cdot{}}} ,
number-unit-product = \ ,
multi-part-units = single ,
}
\usepackage{units}

%Appendix, TOC and Bibliography
\usepackage{appendix}
\renewcommand\appendixtocname{Appendices}
%\usepackage[nottoc]{tocbibind}
\usepackage[lastpage,user]{zref}

%Figures
\usepackage[svgnames]{xcolor} % Required to specify font color
\usepackage{tikz}
\usetikzlibrary{shadings}
\usepackage{float}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[rmargin=2.5cm, tmargin=2.5cm, lmargin=2.5cm, bmargin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{etoolbox}
\usepackage{verbatim}
\usepackage[space]{grffile}
\usepackage[final]{pdfpages}
\usepackage{array}
\usepackage{multirow}

%Header footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{F. G. Kristensen,\\C. V. Sørensen og R. K. F. Wiuff}
\chead{Nanomechanics for graphene membranes\\}
\rhead{10/1-2018\\Course 34029: Physics Project}
\cfoot{Side \thepage\, af \zpageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

%Text tools
\usepackage[normalem]{ulem}
\usepackage{import}
\usepackage{newclude}
\usepackage{url}
\usepackage{lipsum}
\usepackage{microtype}
\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = red %Colour of citations
}
\usepackage[capitalise]{cleveref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{silence}
\WarningFilter{revtex4-1}{Repair the float}

%Definitions and new commands
\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}
\newcommand{\logas}[1]{\log_{_{10}}{\left( #1 \right)}}
\newcommand{\sins}[1]{\sin{\left( #1 \right)}}
\newcommand{\tans}[1]{\tan{\left( #1 \right)}}
\newcommand{\coss}[1]{\cos{\left( #1 \right)}}
\newcommand{\sinas}[1]{\sin{\left( #1 \degr \right)}}
\newcommand{\tanas}[1]{\tan{\left( #1 \degr\right)}}
\newcommand{\cosas}[1]{\cos{\left( #1 \degr\right)}}
\newcommand{\lnas}[1]{\mathrm{ln}\left( #1 \right)}
\newcommand{\degr}{^{\circ}}
\newcommand{\me}{\mathrm{e}}
\newcommand{\eula}[1]{ \dpd{L }{#1} - \dod{}{t}\left(\dpd{L}{\dot{#1}}\right)}

\begin{document}

%Titlepage herunder:
\begin{abstract}
  \begin{description}
  \item[abstract]
  In this paper we will analyse the dynamics and mechanics of carbon nano membranes. To calculate how every atom should be placed and how they react under different circumstances is a long and time consuming task for people doing experimental work. That's why we aim to create, through simulation, comparable data points for further use experimentally.
    \item[Background] Since the isolation and characterisation of
    Graphene in 2004 by Andre Geim and
Konstantin Novoselov, scientists have marvelled over the physical properties and potential
application of Graphene. Being a relatively new material, many aspects and ideas are being
investigated and researched at all times. Graphene yield extreme tensile strength as well as
extreme electric conductivity, yet its structure is fairly simple. Graphene consists solely of
carbon atoms thus making it, as carbon atoms are greatly understood in terms of chemical
bonding, easy to simulate using specialised software. As graphene is a very versatile
material the possibilities for research in simulation enviroments are virtually limitless.
Therefore it is basically possible to make experiments limited only by imagination, in order
to discover new properties and possible applications of graphene. This saves ressources
before entering the lab, where where the simulated reality is tested.
    \item[Purpose] A graphene layer on top of a substrate with different sized and shaped holes, would
form a nanomembrane. It is expected possible to create such a nanomembrane at the
size of few tens of nanometers at Nanotech with Block-copolymer lithography or TEM
structuring of a substrate. In a virtual enviroment, it is possible to simulate phonons
in the graphene atop of these holes in the membrane. The purpose of this project is to
simulate phonons in the nanomembrane and find the optimal conditions for producing
phonons in the terahertz spectrum.
    \item[Method] We will employ the software Atomistic ToolKit (ATK) to calculate phonon properties
of membranes as well as performing molecular dynamics of the excited membrane. The
software will enable prompt setup of relevant structures so that more time is free to analysis
and actual simulations.
    \item[Results] My money's in that office, right? If she start giving me some bullshit about it ain't there, and we got to go someplace else and get it, I'm gonna shoot you in the head then and there.
    \item[Conclusion] My money's in that office, right? If she start giving me some bullshit about it ain't there, and we got to go someplace else and get it, I'm gonna shoot you in the head then and there.
  \end{description}
\end{abstract}

\title{Nanomechanics for graphene membranes}
\date{10/1-2018}
\author{Frederik Grunnet Kristensen (s164003)}
\email[E-mail at ]{s164003@student.dtu.dk}
\author{Christoffer Vendelbo Sørensen (s163965)}
\email[E-mail at ]{s163965@student.dtu.dk}
\author{Rasmus Kronborg Finnemann Wiuff (s163977)}
\email[E-mail at ]{s163977@student.dtu.dk}
\affiliation{Technical University of Denmark}
\homepage[Homepage of the Technical University of Denmark ]{dtu.dk}

\maketitle

\pagenumbering{arabic}

\tableofcontents
\thispagestyle{empty}
\newpage
\setcounter{page}{1}

%Text
\section{Introduciton to Nanomechanics and Atomistix ToolKit}
\input{sections/Intro.tex}
\input{sections/Geometry.tex}
\input{sections/MD.tex}
\input{sections/ATK.tex}
%Text

%Bibliography herunder:
\newpage

\bibliographystyle{unsrtnat}
\bibliography{Bibliography}

\newpage
\listoffigures
\listoftables
\newpage
%Appendicer herunder:
\input{Appendix.tex}
\end{document}
